
# R Markdown/bookdown hints

## Labels and Cross-referencing {#S:LabelAndCrossref}

The following shows how to code Section titles and cross-refer to them.
  
```
## Labels {#S:LabelAndCrossref}
```

With that reference, `S:LabelAndCrossref`, you can readily refer to
Section \@ref(S:LabelAndCrossref) in your text, as follows:

```
With that reference, `S:LabelAndCrossref`, you can readily refer to
Section \@ref(S:LabelAndCrossref) in your text, as follows:
```

The same applies to other components of a book like tables, equations, figures.


For example, the following R Markdown

````markdown
See Figure \@ref(fig:cars-plot).

(ref:cars-plot) A *caption* with $\LaTeX$ math $E = m c^2$.

```{r cars-plot, fig.cap='(ref:cars-plot)', echo=FALSE}`r ''`
par(mar = c(4, 4, .2, .1))
plot(cars)  # a scatterplot
```
````

will result in

See Figure \@ref(fig:cars-plot).

(ref:cars-plot) A *caption* with math $E = m c^2$.

```{r cars-plot, fig.cap='(ref:cars-plot)', echo=FALSE}
par(mar = c(4, 4, .2, .1))
plot(cars)  # a scatterplot
```


See also the [Cross Referencing](https://bookdown.org/yihui/rmarkdown-cookbook/cross-ref.html#cross-ref) Section in the R Cookbook.
